Toward Adaptive GPU Resource Management for Embedded Real-Time Systems

### 2012-03-09 draft/draft.tex
added Section 2 (System Model)

sporadic/periodic tasks etc.
NVIDIA Fermi GPUs.
NVIDIA Kepler GPUs may allow multiple contexts to execute on the GPU
simultaneously.

>>>>

We assume such embedded systems that equip GPUs as compute devices.
The application task starts execution on the CPU, and offloads its
data-parallel compute-intensive workload onto the GPU when needed.
Once offloaded onto the GPU, the task becomes non-preemptive due to many
reasons.
In fact, it is technically possible to preempt the running task on the
GPU by loading and restoring its context, but it requires additional
firmware, runtime, and OS support, and the preemption cost would be
non-trivial due to a very large set of GPU registers and states.
We hence restrict our attention to a non-preemptive execution model for
GPU computing.
GPUs may also pose some constraints in multi-tasking.
Even the NVIDIA Fermi architecture~\cite{Fermi}, one of the most popular
GPU product lines, allows only one context to use GPU resources at
once, though this context may spawn multiple GPU kernels (jobs)
simultaneously.
In other words, if task-level parallelism is required, the entire system
must run in the same context.
We however believe that this constraint will not limit the concept of
this paper.
We can use the same context to exploit concurrent parallel job
executions, and it should be enough to demonstrate a proof of concept. 
We also expect that future product lines will remove this concern.

We consider real-time applications where each task runs in a periodic or
sporadic manner under deadline constraints.
Such a task set and application includes motion planning and 
vision-based perception in state-of-the-art autonomous driving
vehicles.
We also presume the computing demand of each task to be highly
variable.
For example, planning and perception workloads are governed by the
number of objects, the size of data, and the desired quality of output.
These workloads are also well parallelizable using the GPU.
Hence, the autonomous driving tasks and applications are our primary
target, but the contribution of this paper is not limited to those but
is also generally applicable to highly vaiable workloads running on the
GPU.
